Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-10 cbm-rbd-paper.tex
tsetup -> tprep, no update figure, gnowhist figure with more dense grid

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tsetup}{\tau_{\text{setup}}}

@@

We can now derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
However, instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
Let $\tsetup$ be the timespan needed to set up maintenance work,
often referred to simply as setup time.
As soon as $\tausnow$ decreases below $\tsetup$,
a preventive maintenance action is initiated.
This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure}.
%and executed at time $\tnow + \tausnow$.

@@

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle.
(An operational cycle begins with system start-up,
and ends when either a failure of the system occors, or a preventive maintenance is carried out.)
This criterion, as described in Section~\ref{sec:costrate} below in detail,
only assumes that $\Rsysnow(t)$ can be calculated,
and thus is not tied to our choice of component model.
One could also consider other optimality criteria to determine $\tausnow$.
When safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

Section~\ref{sec:optim} then focuses on our choice of component model and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is determined in this situation.
Numerical examples for different failure histories are given in Section~ref{sec:examples}.

@@

A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tsetup$,
the time needed to set up maintenance work.
The system continues to run until maintenance work begins,
and the cycle ends when maintenance work is completed.
When the system fails, instead a corrective maintenance action is triggered,
and the system is down also during the wait until maintenance work begins.
This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
Again, the cycle ends when maintenance work is completed.

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,
We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same condition.
Replacement schemes that do not replace all components need to take into account the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
which we will comment on in the Outlook (Section~\ref{sec:outlook}).

@@

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization of $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \tsysnow < \tau
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
\label{eq:gtau}
\end{align}
Note that for the integral to exist in \eqref{eq:gtau},
$\E[1/\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
We will describe next how we numerically evaluate \eqref{eq:gtau} and find $\tausnow$.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

@@

@@

***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours

>>>>

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tprep}{\tau_{\text{prep}}}

@@

We can now derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
However, instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
Let $\tprep$ be the timespan needed to prepare maintenance work.
As soon as $\tausnow$ decreases below $\tprep$,
a preventive maintenance action is initiated.
This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure}.
%and executed at time $\tnow + \tausnow$.

@@

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle.
(An operational cycle begins with system start-up,
and ends when either a failure of the system occors, or a preventive maintenance is carried out.)
This criterion, as described in Section~\ref{sec:costrate} below in detail,
only assumes that $\Rsysnow(t)$ is given,
and thus is not tied to our choice of component model.
One could also consider other optimality criteria to determine $\tausnow$.
When safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

Section~\ref{sec:optim} then focuses on our choice of component model and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is determined in this situation.
Numerical examples for different failure histories are given in Section~\ref{sec:examples}.

@@

A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tprep$,
the time needed to prepare maintenance work.
The system continues to run until maintenance work begins,
and the cycle ends when maintenance work is completed.
When the system fails, instead a corrective maintenance action is triggered,
and the system is down also during the wait until maintenance work begins.
This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
Again, the cycle ends when maintenance work is completed.

At the end of each cycle,
the component information gained during the completed cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,
We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
such that the system begins a new cycle always under the same condition.
Replacement schemes that do not replace all components need to take into account the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
and we will comment on this in the Outlook (Section~\ref{sec:outlook}).

@@

Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
giving the (random) system failure time for times $t > \tnow$,
conditioned on all information available at $\tnow$,
and $\fsysnow(t)$ be the corresponding density.
Conditional on the realization of $\Tsysnow$, the unit cost rate is 
\begin{align*}
g(\tau \mid \Tsysnow = \tsysnow) &=
\begin{cases}
c_p / \tau  & \text{if } \tsysnow \ge \tau \\
c_u / \Tsys & \text{if } \tsysnow < \tau \,.
\end{cases}
\end{align*}
Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
\begin{align}
\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t\,.
\label{eq:gtau}
\end{align}
Note that for the integral to exist in \eqref{eq:gtau},
$\E[1/\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
For our approach, however, this condition is not relevant,
as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
We will describe next how we numerically evaluate \eqref{eq:gtau} and find $\tausnow$.
%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.

@@

***example figures with very weak prior info, could look different for stronger expert information!

***also example where remaining component type is (close to) exponential,
such that corrective maintenance becomes optimal!

\begin{figure}
\includegraphics[width=\textwidth]{ghistfig1}
\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.}
\label{fig:ghistfig1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig2}
\caption{$\tausnow$, $t^* = \tnow + \tausnow$ and $\gnow(\tausnow)$ as functions of $\tnow$
for the system depicted in Figure~\ref{fig:brakesys-layout},
assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
and $c_u = 1$, $c_p = 0.2$.
$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
dropping at each component failure.
If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
at (absolute) time $8.5$.
As $\tausnow$ does not change dramatically most of the time, $t^*$,
the cost-optimal moment of maintenance on the absolute timescale (top right panel),
steadily increases, with small drops corresponding to drops in $\tausnow$,
indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
differing from the overall cost rate (lower right panel).
%For the maintenance action triggered at $\tnow = 8$,
%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
up from $0.076$ for repair at time $8.62$, as cost-optimal at time $8$.}
\label{fig:tauhistfig2}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{tauhistfig3}
\caption{Illustration of the gains due to the parameter update.
$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
same with $t^*$ (top right panel).
The adaptive algorithm recongnizes the higher reliability of system components,
leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
\label{fig:tauhistfig3}
\end{figure}

@@

***$\tprep$ could vary over time, e.g., longer on weekends or outside office hours
